Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-07-01 semantic-nd/article.tex
Small fixes on conclusion and future work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\label{sec:conclusion}
In this paper we presented how to define a stable novelty threshold function on
top of \emph{probabilistic graphical models} instantiated dynamically from sensed
semantic data.
The presented technique is based on the ratio between a conditional and
unconditional probability and when perfect information exists it performs an optimal
novelty detection threshold.

It was also shown that a correct estimation of unconditional probability plays an
important role specially on small input spaces. Moreover, semi-supervised techniques
implemented with the access to unlabelled data can be used to significantly improve
novelty detection performance.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\label{sec:conclusion}
In this paper we presented how to define a stable novelty threshold function on
top of \emph{probabilistic graphical models} instantiated dynamically from sensed
semantic data.
The presented technique is based on the ratio between a conditional and
unconditional probability and when perfect information exists it performs an optimal
novelty detection threshold under the assumption that $P(novel)$ is constant across
all the graph structures.

It was also shown that a correct estimation of unconditional probability plays an
important role specially on small input spaces. Moreover semi-supervised techniques,
implemented with the access to unlabelled data, can be used to significantly improve
novelty detection performance.
